\documentclass[a4paper,10pt]{article}
\input{glyphtounicode}
\pdfgentounicode=1
\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\geometry{margin=0.35in}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.2\textwidth}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{4pt}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.7}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}
% chktex 8


\begin{document}


\pagestyle{empty}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%----------Header--------------


  \begin{tabularx}{\linewidth}{@{} C @{}}

    \Huge{Suvan Banerjee} \\[7.5pt]

    \href{https://github.com/suvanbanerjee}{\raisebox{-0.05\height}\faGithub\ suvanbanerjee} \ $|$ \ 
    \href{https://linkedin.com/in/suvanbanerjee}{\raisebox{-0.05\height}\faLinkedin\ suvanbanerjee} \ $|$ \  \ 
    \href{mailto:banerjeesuvan@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ banerjeesuvan@gmail.com} \ $|$ \ 
    \href{tel:+919462122507}{\raisebox{-0.05\height}\faMobile \ +91 9462122507}
    \\
    \\
  \end{tabularx}


%----------Education-----------


  \section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Dayananda Sagar College Of Engineering}{SGPA: 9.05}%
        {B.E in Information Science (VTU)}{2022--2026}
        \hspace{4pt}
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
      \resumeSubheading
        {Kendriya Vidyalaya No.1 Bikaner}{87.4\%}
        {CBSE---Higher Secondary/Senior School}{2020--2022} \\
    \resumeSubHeadingListEnd
  \vspace{-15pt}


%----------Skills--------------

\vspace{6pt}
  \section{Skills}
  \begin{tabularx}{\linewidth}{@{}l X@{}}
    \textbf{Languages:} &  \normalsize{Python, C, C++, JavaScript, Bash } \\
    \textbf{Frameworks/Technologies:}  &  \normalsize{Linux, Git, Github, Flask, FastAPI, Cryptography, Docker}\\
  \end{tabularx}
  \vspace{-5pt}


%----------Experience-----------
  
    \section{Experience}
    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \vspace{-5pt}
      \textbf{Opensource}|\textit{Open Voice OS -- Remote (May 2024 - Present)} \\
      \multicolumn{1}{@{}X@{}}{
        \begin{itemize}
          \item Open Voice OS is an open-source voice assistant built on top of Mycroft-core.
          \item Developed entire website using Next.js, Tailwind, along with a blog site, and maintained the same.
          \item Designed 2 plugins for the voice assistant: one for fetching stock prices and a dependency-free VAD plugin.
          \item Assisted with localization, contributed to the installer script, added Zorin OS support by writing Ansible roles.
        \end{itemize}} \vspace{-7pt} \\
    \end{tabularx}
    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \vspace{-5pt}
      \textbf{Full Stack Intern}|\textit{Burdenoff -- Remote (July 2024 - Present)} \\
      \multicolumn{1}{@{}X@{}}{
        \begin{itemize}
          \item Burdenoff is a private consultancy firm that provides services medium to large scale businesses.
          \item My role is to develop and maintain Ramco Technologies' website and develop a cms for the same.
          \item Setup the boilerplate for an e-commerce website using Medusa and Next.js and developed the same.
        \end{itemize}} \vspace{-7pt} \\
    \end{tabularx}    


%----------Projects------------


  \section{Projects}
    
    \vspace{7pt}
    
  \begin{tabularx}{\linewidth}{ @{}l r@{} }

    \vspace{-5pt}
    \textbf{Project Zeta}|\textit{Flask, Supabase} & \hfill \href{https://projectzeta.vercel.app/}{Deployed} \\
    \multicolumn{1}{@{}X@{}}{
    \begin{itemize}
        \item A web platform for teachers where they can create their own ctf like challenges.
        \item Utilized Flask for backend and Supabase for database.
        \item Proof of concept for a new way of teaching cybersecurity using a gamified approach.
    \vspace{-10pt} 
        \end{itemize} 
        \vspace{-7pt} 
        }  \\

\vspace{-5pt}
    \textbf{Smart Traffic Management System} | \textit{Python, Pyfirmata, ftplib} & \hfill \href{https://github.com/suvanbanerjee/Smart-Traffic-System}{GitHub} \\
      \multicolumn{1}{@{}X@{}}{
        \begin{itemize}
            \item Utilized computer vision (yolo v8) for adaptive traffic signal control and real-time traffic density calculation.
            \item Utilized Arduino Uno to control traffic lights, enhancing traffic management and signal synchronization.
            \item Implemented WLAN data transfer using FTP to send real-time traffic density information for signal and data logging and utilized parallel computing for efficient data processing and traffic management \vspace{-10pt} 
        \end{itemize}
            }  \\

\vspace{-5pt}
    \textbf{WeatherKit} | \textit{Python, API, Web Scraping} & \hfill
    \href{https://pypi.org/project/weatherkit/}{PyPi}
    \\
    \multicolumn{1}{@{}X@{}}{
    \begin{itemize}
        \item A weather forecasting tool that provides weather without API key.
    \item Utilized Meteo API and web scraping to provide accurate weather information.
    \item Developers can use address or location coordinates to get weather and forecast information.
    \vspace{-10pt} 
    \end{itemize}
        }  \\ 
  \end{tabularx}


%----------Achievements---------


  \section{Achievements and Certifications}


    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{Google Cybersecurity} & \hfill \href{https://www.coursera.org/account/accomplishments/professional-cert/GZJ7LQGCFFZF}{Coursera (Mar 2024)}
      \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{An eight course professional certificate program in cybersecurity. Equipped with skills in threat detection, incident response, network security, python automation, SQL etc. }
    \end{tabularx}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{AI Security Fundamentals} & \hfill \href{https://security.certificates.lakera.ai/credentials/c46521d6-5748-4834-8bac-ecf7913c3ccc}{LakeraAI (Mar 2024)}
      \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{AI Security Course, covering topics such as GenAI threats, cybersecurity frameworks, AI application security, LLM red teaming, and AI governance. }
    \end{tabularx}

%----------Extracurricular----------


  \section{Extracurricular}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{St. Broseph Foundation --- Volunteer, Tech Team} & \hfill Dec 2022 - Feb 2023 \\[3.75pt]
    \multicolumn{2}{@{}X@{}}{Support citizens of Bengaluru by developing and maintaining internal tools as part of the tech team, and assist with day-to-day activities at HQ.}
    \end{tabularx}


    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{PointBlank --- Member} & \hfill Dec 2022 - Present \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{PointBlank is a group of over 80 programmers who work to promote coding culture in colleges by participating in more than 10 contests and organising technical seminars}
    \end{tabularx}


    \end{document}